
\documentclass[12pt]{article}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,pdflscape,array,indentfirst,booktabs,placeins,rotating,adjustbox,multirow,makecell}

\usepackage{hyperref}
\usepackage[flushleft]{threeparttable}
\usepackage[labelfont=bf]{caption}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage[authoryear]{natbib}
\usepackage{soul}
\usepackage[position=bottom]{subfig}
\usepackage{setspace}
\usepackage{enumerate}
\usepackage{enumitem}

%\normalem

%\onehalfspacing
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}{Proposition}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newtheorem{hyp}{Hypothesis}
\newtheorem{subhyp}{Hypothesis}[hyp]
\renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}

\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}

%\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{C}[1]{>{\centering\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}m{#1}}

\geometry{left=0.75in,right=0.75in,top=0.75in,bottom=0.75in}

\usepackage[T1]{fontenc} % section title

% -------- Define new color ------------------------------
\usepackage{color}  
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{mygrey}{rgb}{0.85,0.85,0.85} % make grey for the table
\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
% --------------------------------------------------------

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=darkred,      
	urlcolor=cyan,
	%	footnotecolor=black,
	citecolor=blue
}

% define footnote color
%\makeatletter
%\def\@footnotecolor{red}
%\define@key{Hyp}{footnotecolor}{%
% \HyColor@HyperrefColor{#1}\@footnotecolor%


\def\@footnotemark{%
	\leavevmode
	\ifhmode\edef\@x@sf{\the\spacefactor}\nobreak\fi
	\stepcounter{Hfootnote}%
	\global\let\Hy@saved@currentHref\@currentHref
	\hyper@makecurrent{Hfootnote}%
	\global\let\Hy@footnote@currentHref\@currentHref
	\global\let\@currentHref\Hy@saved@currentHref
	\hyper@linkstart{footnote}{\Hy@footnote@currentHref}%
	\@makefnmark
	\hyper@linkend
	\ifhmode\spacefactor\@x@sf\fi
	\relax
}%
\makeatother

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=darkred,      
	urlcolor=cyan
}

\usepackage[dvipsnames]{xcolor}

\sectionfont{\color{Violet}} % MidnightBlue RoyalBlue
\subsectionfont{\color{Violet}}
\subsubsectionfont{\color{Violet}}

\renewcommand{\refname}{\textsc{References}}

\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}

% Indent the reference
\makeatletter
\renewcommand\@biblabel[1]{}
\renewenvironment{thebibliography}[1]
{\section*{\refname}%
	\@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
	\list{\@biblabel{\@arabic\c@enumiv}}%
	{\settowidth\labelwidth{\@biblabel{#1}}%
		\leftmargin\labelwidth
		\advance\leftmargin\labelsep
		\advance\leftmargin by 2em%
		\itemindent -2em% 
		%\itemindent-\labelsep
		\@openbib@code
		\usecounter{enumiv}%
		\let\p@enumiv\@empty
		\renewcommand\theenumiv{\@arabic\c@enumiv}}%
	\sloppy
	\clubpenalty4000
	\@clubpenalty \clubpenalty
	\widowpenalty4000%
	\sfcode`\.\@m}
{\def\@noitemerr
	{\@latex@warning{Empty `thebibliography' environment}}%
	\endlist}
\makeatother

% allow in-text math break (MUST install)
\makeatletter
\def\old@comma{,}
\catcode`\,=13
\def,{%
	\ifmmode%
	\old@comma\discretionary{}{}{}%
	\else%
	\old@comma%
	\fi%
}
\makeatother

\begin{document}
	\title{Suggested title of our paper:\\ \vspace{4mm} {\sc \bf  Informationally Sensitive Debt and Monetary–Fiscal Interactions}}
	
	\date{\small This Version: \today }
	
	\maketitle

\doublespacing


Our framework studies the joint determination of inflation, sovereign risk, and fiscal  issuance in an environment where the central bank conducts balance sheet policies,  the fiscal authority issues nominal debt, and private agents form beliefs about  default risk under asymmetric information. This environment combines features that have typically been studied separately in the sovereign risk and monetary policy  literature. I think it is worthwhile pursuing what we have done so far.

I think that the paper closet to ours is that of \citet{Bassetto2025}, which I describe below among other relevant papers.
%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Informationally Sensitive Debt and Monetary--Fiscal Policy Interactions}

A growing literature studies how sovereign debt can become informationally sensitive and how beliefs about fiscal backing, policy credibility, and monetary–fiscal interactions determine inflation and sovereign risk. This literature emphasizes that inflation dynamics and debt valuation depend not only on fiscal fundamentals but also on expectations about future policy, institutional credibility, and the informational environment faced by investors. 

Several recent contributions highlight different mechanisms through which beliefs affect inflation and sovereign risk, including \citet{bassetto2019inflation}, \citet{Bassetto2025}, \citet{BianchiIlut2017}, \citet{BianchiMondragon2022}, and \citet{ArellanoBaiMihalache2025}. These papers build on earlier work on expectations-driven crises and fiscal price level determination such as \citet{Calvo1988}, \citet{ColeKehoe2000}, \citet{Uribe2006}, and \citet{CorsettiDedola2016}. 

While these contributions share the idea that beliefs about fiscal backing and policy credibility can drive inflation and sovereign risk, they differ in their modeling of agents, assets, information frictions, and policy interactions. Some papers emphasize endogenous information acquisition, others heterogeneous information across investors, others regime uncertainty and credibility, and more recent work embeds sovereign risk within New Keynesian environments. The following sections discuss these contributions in detail.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsubsection*{Comparison with \citet{Bassetto2025}}

\citet{Bassetto2025} develop a model in which informational frictions generate sudden inflation episodes. Their framework explains why inflation may remain largely disconnected from fiscal imbalances for extended periods and then adjust abruptly once fiscal fundamentals deteriorate sufficiently. The model builds on \citet{mackowiak2015business} and emphasizes the role of costly information acquisition and informationally sensitive debt. A central contribution of the paper is to show that inflation dynamics may exhibit long periods of stability followed by sudden jumps, even when fiscal fundamentals evolve smoothly. These dynamics arise because information about fiscal sustainability is endogenously acquired rather than freely available, which introduces non-linearities in belief formation and asset pricing.

\paragraph{Agents.}

The economy features a representative household that saves using nominal government bonds and decides whether to acquire costly information about future fiscal surpluses. Agents face a trade-off between remaining inattentive and paying information costs to learn about fiscal fundamentals. This endogenous attention decision introduces non-linearities in belief formation and asset pricing. When fiscal conditions are perceived to be stable, agents find it optimal to remain inattentive, since the benefits of acquiring additional information are small. However, as fiscal risks increase, the value of acquiring information rises, leading to sudden changes in attention and belief updating. Because agents are otherwise identical, the model abstracts from financial intermediation and from heterogeneity in asset access. As a result, inflation dynamics arise from aggregate belief changes rather than from differences in portfolio composition across agents. The representative agent structure allows the model to isolate the informational channel driving inflation without introducing additional heterogeneity across financial institutions.

\paragraph{Time Horizon and Timing.}

The model features a finite three-period structure. The first period represents the initial environment in which agents hold nominal government debt and form prior beliefs about fiscal fundamentals. In the second period, agents decide whether to acquire costly information and update beliefs accordingly. In the final period, fiscal outcomes are realized and debt repayment occurs. This timing structure allows the model to highlight how information acquisition decisions affect inflation dynamics and debt valuation. The finite horizon also simplifies the analysis of belief updating and the transition between informationally insensitive and informationally sensitive regimes.

\paragraph{Assets and Who Issues Them.}

Nominal government bonds are the only financial asset in the model. These bonds provide a store of value across periods and their valuation depends on expectations about future fiscal surpluses. Because nominal debt is subject to inflation risk, its real value depends on beliefs about fiscal backing and future price level determination. There is no explicit distinction between fiscal and monetary liabilities, and the central bank balance sheet is not modeled separately. This simplified asset structure allows the authors to isolate how expectations about fiscal sustainability influence debt valuation and inflation dynamics. The absence of additional financial assets also implies that portfolio allocation decisions operate solely through government bonds, which magnifies the effect of belief changes on bond prices and inflation.

\paragraph{Monetary Policy.}

\blue{Monetary policy is modeled parsimoniously rather than omitted. In the baseline, the nominal interest rate is pegged, and inflation depends on beliefs about whether future fiscal backing is sufficiently strong to sustain a low-inflation outcome. When fiscal capacity is ample, the future price level can remain tied to a stable monetary target. When fiscal backing is constrained, inflation adjusts to restore solvency. The paper therefore studies sudden inflations through the interaction of information acquisition and the monetary--fiscal regime, not through the absence of monetary policy altogether.}

\paragraph{Fiscal Policy.}

\blue{Fiscal policy operates through the future surpluses that back nominal debt, but its role is not merely passive. The central distinction is whether taxes and surpluses adjust to validate a low-inflation monetary outcome or whether the price level must adjust because fiscal backing is limited. Government debt is inherited rather than strategically issued, yet the interaction between fiscal capacity, regime beliefs, and information acquisition is central to the inflation outcome.}

\paragraph{Informational Asymmetries.}

The informational friction arises from costly information acquisition. Agents decide whether to acquire information about future fiscal surpluses, and this decision depends on the expected benefits of information. When fiscal fundamentals deteriorate sufficiently, agents become more willing to acquire information, making debt informationally sensitive. This endogenous information acquisition generates periods of inattention followed by sudden increases in information gathering. As more agents acquire information, beliefs about fiscal sustainability become more responsive to fiscal news, which amplifies the effect of fiscal shocks on inflation. This mechanism generates non-linear belief dynamics and sudden changes in inflation expectations.



\paragraph{Economic Mechanism.}

\blue{The central mechanism in \citet{Bassetto2025} arises from the interaction between costly information acquisition and the valuation of nominal government debt. Nominal debt behaves like an option-like asset whose real payoff depends on whether future fiscal backing is sufficient or whether inflation must absorb fiscal stress. When fiscal fundamentals are strong, agents remain relatively inattentive because the benefits of information are small, and inflation is weakly responsive to fiscal news.}

\blue{As fiscal fundamentals deteriorate, the value of information rises. Once fiscal stress becomes sufficiently important, agents pay attention to future surpluses, debt becomes informationally sensitive, and small changes in fiscal news lead to large revisions in inflation expectations. This is what generates the paper's sudden-inflation episodes.}

\blue{Complementarities in information acquisition can further amplify these dynamics and may create regions with multiple information-acquisition equilibria. The paper's contribution is therefore to show how gradual movements in fiscal fundamentals can interact with endogenous attention and regime beliefs to produce abrupt changes in inflation dynamics.}




%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Comparison with \citet{ArellanoBaiMihalache2025}}

\blue{\citet{ArellanoBaiMihalache2025} develop a New Keynesian sovereign-default model for an emerging-market small open economy. Their framework integrates pricing frictions, an interest-rate rule, and external sovereign default, and it emphasizes two key mechanisms: default risk creates inflation pressures through expectations, and tight monetary policy disciplines sovereign borrowing. The paper therefore studies how monetary policy and sovereign risk interact even when sovereign debt is denominated in foreign currency and inflation does not directly dilute the government's debt burden.}

\paragraph{Agents.}

\blue{The model features households, firms, a monetary authority, and a government subject to sovereign default risk. Households consume and supply labor, firms set prices subject to nominal rigidities, and the government borrows abroad and decides whether to default. The key sovereign liability is held by foreign lenders, so the paper is not about heterogeneous domestic holders of defaultable government debt.}

\paragraph{Time Horizon and Timing.}

\blue{The framework operates in an infinite-horizon environment with forward-looking agents. Each period, households and firms make standard New Keynesian decisions, the monetary authority sets the nominal interest rate through a policy rule, and the government chooses external borrowing and default. Default decisions depend on current debt and on how today's choices affect future inflation, consumption, and borrowing conditions.}

\paragraph{Assets and Who Issues Them.}

\blue{The government borrows externally using long-term sovereign debt denominated in foreign currency. Foreign investors price this debt based on expected repayment probabilities, generating endogenous sovereign spreads. Domestic nominal bonds appear in the household side of the model but clear in zero net supply, so the central defaultable liability is external debt rather than nominal government debt held domestically. The framework does not explicitly model reserves or central bank balance sheet policies.}

\paragraph{Monetary Policy.}

\blue{Monetary policy follows a Taylor-type rule. Sovereign risk modifies transmission because default risk affects firms' pricing decisions and households' intertemporal conditions. A central result of the paper is that tighter monetary policy can discipline sovereign borrowing: by raising monetary distortions, it reduces the government's incentive to overborrow and can bring spreads down. The relevant trade-off is therefore not simply that tightening raises spreads through borrowing costs, but that monetary policy can discipline fiscal behavior while stabilizing inflation.}

\paragraph{Fiscal Policy.}

\blue{Fiscal policy is characterized by optimal external borrowing and default decisions inside a dynamic sovereign-default problem. The government internalizes how borrowing changes future spreads and how default risk feeds back into inflation and activity. There is no signaling motive, but borrowing is still an endogenous strategic choice rather than a purely mechanical response to financing needs.}

\paragraph{Informational Asymmetries.}

\blue{The model assumes full information. All agents observe fiscal fundamentals, borrowing costs, and default risk. There is no asymmetric information about government type or policy intentions. Sovereign spreads arise from equilibrium pricing of default risk rather than from informational frictions or signaling mechanisms.}



\paragraph{Economic Mechanism.}

\blue{The central mechanism in \citet{ArellanoBaiMihalache2025} combines default amplification and monetary discipline. Higher default risk raises expected future inflation and lowers expected future consumption, which creates current inflation pressures and depresses activity through forward-looking pricing and consumption decisions.}

\blue{Monetary policy then feeds back into sovereign risk because tighter policy raises the monetary distortions associated with borrowing and thereby discourages overborrowing. This can reduce spreads and default probabilities in equilibrium. The paper therefore shows that sovereign risk changes both inflation dynamics and the design of monetary policy, and that strict inflation targeting need not be optimal once sovereign default risk is present.}

%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Comparison with \citet{bassetto2019inflation}}

\blue{\citet{bassetto2019inflation} study how heterogeneous information interacts with the currency denomination of government debt. Their framework compares environments in which repayment problems are resolved through outright default or through inflation, and it shows how the identity and information of marginal traders affect the sensitivity of debt prices to bad fiscal news.}

\paragraph{Agents.}

\blue{The model features agents with dispersed private information rather than a simple informed-versus-uninformed split. In the key environments, sophisticated bond traders interact with a broader set of agents whose beliefs matter for future pricing, and the way information enters prices depends on whether crisis resolution occurs through default or inflation.}

\paragraph{Time Horizon and Timing.}

\blue{The core model is a finite-horizon Bayesian trading environment rather than an infinite-horizon debt accumulation problem. The paper studies how information is incorporated into prices across a small number of periods, and how price sensitivity differs between inflationary and default-type debt structures.}



\paragraph{Assets and Who Issues Them.}

\blue{The paper contrasts debt exposed to inflation risk with debt exposed to outright default risk. Its comparison is not a rich optimal debt-composition problem in which the government jointly chooses domestic- and foreign-currency debt shares. Instead, the paper uses the Euro-versus-Yen contrast to isolate how information affects the pricing of defaultable versus inflation-sensitive debt.}


\paragraph{Monetary Policy.}

It is not modeled through an explicit policy rule or central bank balance sheet. Instead, inflation is determined endogenously through the government’s intertemporal budget constraint and investor expectations about fiscal sustainability. The price level adjusts to ensure the real value of nominal government liabilities is consistent with expected future fiscal surpluses. 

Because there is no explicit central bank reaction function, inflation dynamics emerge from fiscal incentives and belief formation. When fiscal fundamentals are strong, investors expect repayment through future surpluses and inflation remains stable. As fiscal conditions deteriorate, investors anticipate inflationary dilution of nominal debt, leading to rising inflation expectations and sovereign risk premia.

\paragraph{Fiscal Policy.}

\blue{Fiscal policy is deliberately stylized. The paper is not centered on a rich intertemporal fiscal optimization problem, but on how a given solvency problem is priced when repayment occurs through inflation in one environment and through default in another. This lets the authors isolate the role of information rather than the effects of endogenous strategic debt issuance.}



\paragraph{Informational Asymmetries.}

\blue{Information heterogeneity plays a central role, but the friction is dispersed private information rather than costly attention. Agents receive signals with different relevance for future pricing, and the paper studies how these informational asymmetries translate into different price responses under inflationary versus default-type debt.}



\paragraph{Economic Mechanism.}

\blue{The paper's key mechanism is that the sensitivity of debt prices to bad news depends on who will be pivotal in future trading. In default-type environments, prices are shaped by relatively sophisticated traders; in inflationary environments, prices are influenced by a broader and less informed group. Because of this asymmetry, inflation-sensitive debt can be more resilient to bad news even when the underlying fiscal loss is the same.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Comparison with \citet{BianchiIlut2017}}

\blue{\citet{BianchiIlut2017} study how beliefs about the monetary--fiscal policy mix affect inflation, debt dynamics, and long-bond prices in the US Great Inflation. Their framework integrates recurrent policy-regime changes into a DSGE model and emphasizes that inflation outcomes depend not only on current policy behavior but also on beliefs about which authority will stabilize debt in the future.}

\paragraph{Agents.}

The model features representative households and firms within a standard New Keynesian framework. Households make consumption, labor supply, and saving decisions, while firms operate under monopolistic competition and face nominal rigidities in price setting. These nominal rigidities generate the standard New Keynesian transmission channels for monetary policy. Financial markets are competitive and complete, and there is no segmentation across agents or differences in access to financial assets. As a result, macroeconomic dynamics are driven by aggregate expectations about policy regimes rather than by heterogeneity in financial positions or balance sheet exposure across agents.

\paragraph{Time Horizon and Timing.}

\blue{The model operates in an infinite-horizon stochastic environment in which policy regimes evolve according to a Markov process. Each period, agents form expectations about future regime transitions and incorporate these expectations into current decisions. The infinite-horizon structure allows beliefs about distant future policy behavior to affect current inflation, debt dynamics, and bond prices. This dynamic environment generates persistent interactions between policy credibility, expectations, and macroeconomic outcomes.}

\paragraph{Assets and Who Issues Them.}

\blue{Government bonds are central because the paper studies debt dynamics and long-bond valuation under alternative monetary--fiscal regimes. The model does not emphasize a central bank balance sheet; instead, the interaction between policy authorities operates through inflation, debt stabilization, and the valuation of government bonds, especially long-term bonds.}

\paragraph{Monetary Policy.}

\blue{Monetary policy follows a Taylor-type rule, but the paper allows for three policy regimes rather than a simple monetary-dominance versus fiscal-dominance dichotomy. In the language of Leeper (1991), the regimes are active monetary/passive fiscal, passive monetary/active fiscal, and active monetary/active fiscal. This third conflict regime is important because it governs how agents think debt will eventually be stabilized when both authorities behave aggressively.}

\paragraph{Fiscal Policy.}

\blue{Fiscal policy is represented through rules governing taxation, government spending, and debt stabilization. The fiscal authority adjusts taxes or surpluses in response to debt levels, but the responsiveness of fiscal policy depends on the prevailing regime. Under fiscally led regimes, fiscal policy becomes less responsive to debt, which changes how agents expect debt to be stabilized and therefore alters inflation and bond-pricing outcomes. Fiscal policy therefore interacts with monetary policy through expectations about future regime behavior rather than through strategic issuance or explicit default decisions.}

\paragraph{Informational Asymmetries.}

\blue{Agents face regime uncertainty, but not private-information asymmetry. They form expectations over recurrent Markov-switching regimes and understand that the policy mix may change over time. The beliefs channel therefore works through rational expectations about future regime changes rather than through signal extraction or heterogeneous private information.}



\paragraph{Economic Mechanism.}

\blue{The central mechanism in \citet{BianchiIlut2017} is driven by beliefs about which authority will ultimately stabilize debt. When agents assign greater probability to fiscally led regimes, fiscal imbalances become inflationary, long-bond prices fall, and real rates and debt dynamics adjust accordingly. The paper's emphasis is therefore on inflation, debt, and bond valuation, not on sovereign default spreads.}

\blue{A key result is that disinflation succeeds only when monetary tightening is backed by fiscal policy. Beliefs about future regime changes matter because they alter how current fiscal shocks feed into inflation and bond prices. The paper thus shows that credibility about the future policy mix is central to understanding the rise and fall of inflation.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Comparison with \citet{BianchiMondragon2022}}

\blue{\citet{BianchiMondragon2022} study how the loss of monetary independence affects vulnerability to self-fulfilling rollover crises. Their framework combines sovereign default, rollover multiplicity, foreign-currency debt, and nominal rigidities, and it highlights how the inability to use monetary policy for macroeconomic stabilization can make investor panics more likely to trigger default.}

\paragraph{Agents.}

\blue{The model features domestic households, firms, a government, and foreign lenders. Expectations matter because foreign lenders may run on government debt, while domestic macroeconomic conditions determine whether repayment remains attractive for the government. The paper is therefore not best described as a homogeneous-investor model centered on inflation risk.}

\paragraph{Time Horizon and Timing.}

\blue{The framework operates in an infinite-horizon environment with repeated debt rollover and the possibility of self-fulfilling crises. Investors decide whether to lend before the government decides whether to repay or default, so pessimistic beliefs can become self-validating. This timing is central to the rollover-crisis mechanism.}

\paragraph{Assets and Who Issues Them.}

\blue{The government issues long-term sovereign debt, and in the baseline this debt is denominated in real terms or, equivalently, in foreign currency. Because the debt cannot be inflated away in the baseline, the central monetary issue is macroeconomic stabilization under nominal rigidities rather than debt dilution through inflation.}

\paragraph{Monetary Policy.}

\blue{Monetary policy is characterized by the degree of monetary independence. When the government can use the exchange rate or monetary policy to stabilize output and employment during a crisis, repayment is more attractive and rollover crises are less likely. When monetary policy is constrained, a panic-induced fiscal contraction causes a deeper recession, which makes default more attractive and validates lenders' pessimism.}

\paragraph{Fiscal Policy.}

\blue{Fiscal policy is characterized by debt issuance, taxation, and the need to roll over debt in the face of possible market panics. When lenders refuse to roll over debt, the government must service maturing obligations through fiscal adjustment alone. Under nominal rigidities, that contraction depresses activity and can push the government toward default.}

\paragraph{Informational Asymmetries.}

\blue{The model assumes common information among investors. All agents observe fiscal fundamentals and policy behavior, and there is no asymmetric information about government type or policy intentions. Instead, expectations are driven by common beliefs about whether a panic would trigger a sufficiently severe recession to make default optimal.}



\paragraph{Economic Mechanism.}

\blue{The central mechanism in \citet{BianchiMondragon2022} is an expectations-driven rollover crisis operating through recession amplification. If lenders panic and refuse to roll over debt, the government must engineer a fiscal contraction to repay maturing debt. Under nominal rigidities, that contraction lowers demand and employment, making repayment less attractive and validating the initial panic.}

\blue{Monetary independence matters because it lets the government use the exchange rate or monetary policy as a shock absorber, reducing the recession associated with a funding crisis. When that policy tool is absent, rollover crises become more likely. The paper therefore emphasizes macro stabilization and self-fulfilling default risk, not inflationary accommodation of government debt.}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{\blue{Comparison with \citet{EspinoKozlowskiMartinSanchez2025}}}

\blue{\citet{EspinoKozlowskiMartinSanchez2025} develop a sovereign-default model with distortionary fiscal and monetary policies for an emerging-market small open economy. Their framework shows how sovereign risk, inflation, exchange-rate depreciation, and domestic distortions move together when governments finance themselves with taxes, money creation, and external debt.}

\paragraph{\blue{Agents.}}

\blue{The paper studies a small open economy with representative infinitely lived households, firms producing tradable and nontradable goods, a government that chooses fiscal and monetary policy, and foreign risk-neutral lenders. The government's problem includes borrowing, taxation, money creation, and default.}

\paragraph{\blue{Time Horizon and Timing.}}

\blue{The environment is infinite-horizon and recursive in discrete time. Each period the government chooses policies without commitment to future debt repayment or future policy actions, and aggregate shocks such as terms-of-trade or productivity shocks affect borrowing conditions and macro outcomes.}

\paragraph{\blue{Assets and Who Issues Them.}}

\blue{The government issues external sovereign debt in foreign currency to foreign investors. Domestic government liabilities take the form of fiat money used for transactions. This distinction matters: inflation does not primarily work by eroding a stock of domestic nominal sovereign bonds, but through money creation, exchange-rate depreciation, and domestic distortions.}

\paragraph{\blue{Monetary Policy.}}

\blue{Monetary policy is implemented through money growth in a cash-in-advance environment for nontradable consumption. The paper studies when monetary policy is actively used to support fiscal policy and shows that distortionary inflation arises when the government lacks lump-sum financing and cannot commit. This is not a central-bank-balance-sheet model with reserves, interest on reserves, or open-market operations.}

\paragraph{\blue{Fiscal Policy.}}

\blue{Fiscal policy uses distortionary labor taxes, public expenditure, transfers, and external borrowing. A generalized Euler equation characterizes debt choice. The debt decision reflects distortion smoothing, default premia, and the interaction between future distortions and current money demand.}

\paragraph{\blue{Informational Asymmetries.}}

\blue{The paper does not rely on asymmetric information, private types, or signaling. The main friction is lack of commitment, not hidden information.}

\paragraph{\blue{Economic Mechanism.}}

\blue{Adverse shocks raise the cost of rolling over external debt. In response, the government reduces debt, raises taxes, lowers spending, increases money creation, and allows faster currency depreciation. The paper's central contribution is to explain the joint movement of sovereign spreads, inflation, currency depreciation, and procyclical fiscal policy in emerging markets when distortionary domestic policies interact with sovereign default risk.}

\subsubsection*{\blue{Comparison with \citet{HurtadoNunoThomas2022}}}

\blue{\citet{HurtadoNunoThomas2022} study how discretionary inflation affects sovereign debt sustainability and welfare in a small open economy with nominal government debt. Their framework compares outright default with inflation as a form of partial default and asks when the ability to inflate away debt improves repayment incentives and welfare.}

\paragraph{\blue{Agents.}}

\blue{The paper studies a small open economy with risk-averse domestic households, a benevolent government, and foreign investors who price sovereign bonds. The government chooses fiscal and monetary policy under discretion and can default outright.}

\paragraph{\blue{Time Horizon and Timing.}}

\blue{The framework is continuous time and infinite horizon. The government repeatedly chooses inflation, borrowing, and default under no commitment, and the debt-income state determines how close the economy is to the default frontier.}

\paragraph{\blue{Assets and Who Issues Them.}}

\blue{The government issues long-term nominal bonds denominated in domestic currency to foreign investors. Because the debt is nominal, inflation can erode its real value. This is crucial to the paper's comparison between outright default and inflation as a partial default instrument.}

\paragraph{\blue{Monetary Policy.}}

\blue{Monetary policy is the discretionary choice of inflation, subject to welfare costs. The paper does not model a central bank balance sheet, reserves, or an interest-rate rule. Instead, it studies the trade-off between using inflation to stabilize debt and the inflationary bias created by discretion.}

\paragraph{\blue{Fiscal Policy.}}

\blue{Fiscal and monetary choices are jointly determined under discretion. The government chooses borrowing and can default, while inflation changes the repayment region by reducing the real burden of nominal debt. The fiscal side is therefore endogenous, but the paper is not about signaling through issuance.}

\paragraph{\blue{Informational Asymmetries.}}

\blue{The paper assumes full information. There are no private types, noisy signals, or asymmetric-information mechanisms.}

\paragraph{\blue{Economic Mechanism.}}

\blue{Inflation acts as a state-contingent partial default that can substitute for outright default. This enlarges the repayment region and can raise welfare near the default frontier because inflation is a more flexible tool than outright default. Over the long run, however, the welfare gains are modest because inflationary bias remains costly when debt stress is low.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{What Is Genuinely New}

Our framework introduces a combination of features that, while individually related to elements studied in the literature, have not been analyzed jointly. In particular, existing papers typically emphasize either informational frictions, sovereign risk, or monetary–fiscal interactions, but rarely integrate these components within a unified framework featuring endogenous debt issuance, central bank balance sheet policies, and signaling.

\paragraph{Central Bank Balance Sheet and Monetary Implementation.}

A first distinguishing feature of our framework is the explicit modeling of the central bank balance sheet. The central bank issues reserves, pays interest on reserves, conducts open market operations, and remits profits to the fiscal authority. These balance sheet interactions create a direct link between monetary policy implementation and fiscal resources, allowing monetary policy to affect fiscal outcomes beyond standard interest rate channels. One can argue that this channel is becoming less important after the global financial crises when QE was enacted, and teh size of teh central bank's balance sheet ballooned.

These institutional features are largely absent in the informationally sensitive debt literature. For example, \citet{Bassetto2025} and \citet{bassetto2019inflation} abstract from central bank balance sheets and model inflation as determined by fiscal backing and expectations. Similarly, \citet{BianchiIlut2017} and \citet{BianchiMondragon2022} model monetary policy through interest rate rules or credibility regimes without explicitly modeling reserves or balance sheet interactions. 

Even in \citet{ArellanoBaiMihalache2025}, which incorporates sovereign risk into a New Keynesian environment, the central bank operates through a conventional Taylor rule and does not explicitly model reserves, balance sheet policies, or remittances. As a result, monetary–fiscal interactions in that framework arise through interest rate effects on sovereign spreads rather than through balance sheet interactions between monetary and fiscal authorities.

\paragraph{Endogenous Nominal Debt Issuance.}

A second novel feature is that the fiscal authority optimally chooses nominal debt issuance. Debt issuance affects financing needs, default incentives, and beliefs about fiscal sustainability. This strategic issuance decision introduces an additional channel through which fiscal policy interacts with inflation and sovereign risk.

Most existing papers abstract from endogenous issuance decisions. In \citet{Bassetto2025}, government debt is inherited and fiscal policy operates through expectations about future surpluses. In \citet{BianchiIlut2017}, fiscal policy is modeled through tax and surplus rules rather than issuance choices. In \citet{BianchiMondragon2022}, the emphasis is on rollover risk rather than optimal issuance. 

Similarly, in \citet{ArellanoBaiMihalache2025}, debt issuance is driven by financing needs and borrowing constraints rather than by strategic signaling or equilibrium selection. Debt evolves endogenously in response to fiscal shocks, but the fiscal authority does not choose issuance to influence beliefs or inflation outcomes.

\paragraph{Sovereign Default and Inflation Interaction.}

Our framework allows inflation to affect repayment incentives and default risk directly. Inflation reduces the real value of nominal debt, which alters the incentives to repay and influences sovereign risk. This creates a joint determination of inflation and sovereign default risk.

While \citet{bassetto2019inflation} consider the interaction between inflation and default, their framework focuses on heterogeneous information and currency denomination of debt rather than monetary–fiscal interactions through central bank balance sheets. 

Similarly, \citet{ArellanoBaiMihalache2025} study sovereign default risk in a New Keynesian environment and show how monetary policy affects default probabilities through borrowing costs. However, inflation affects default risk indirectly through macroeconomic dynamics rather than directly through the real value of nominal debt and strategic issuance decisions. Moreover, their framework does not incorporate informational frictions or signaling mechanisms.

\paragraph{Asymmetric Information and Signaling Through Issuance.}

Another key feature of our framework is the introduction of asymmetric information about government type. Debt issuance becomes a signaling device through which the fiscal authority conveys private information about fiscal fundamentals or repayment incentives.

This informational structure differs from those studied in the literature. \citet{Bassetto2025} emphasize costly information acquisition by agents, while \citet{bassetto2019inflation} emphasize heterogeneous information across investors. \citet{BianchiIlut2017} introduce regime uncertainty, and \citet{BianchiMondragon2022} emphasize credibility and expectations about future policy. 

By contrast, \citet{ArellanoBaiMihalache2025} assume full information and focus on sovereign default risk within a New Keynesian framework. In their model, sovereign spreads arise from equilibrium pricing of default risk rather than from signaling or asymmetric information. As a result, their framework does not generate informationally sensitive debt through signaling mechanisms.

\paragraph{Monetary–Fiscal Interaction Through Policy Rules and Balance Sheets.}

Our framework also introduces a richer interaction between monetary and fiscal policy. Monetary policy operates through reserve remuneration and potentially a Taylor-type rule, while fiscal policy operates through endogenous debt issuance and repayment decisions. Inflation must therefore satisfy both monetary and fiscal equilibrium conditions.

In contrast, existing papers typically focus on one dimension of monetary–fiscal interaction. \citet{BianchiIlut2017} emphasize regime switching between monetary and fiscal dominance. \citet{BianchiMondragon2022} focus on monetary credibility and rollover risk. \citet{ArellanoBaiMihalache2025} highlight how monetary policy affects sovereign spreads through borrowing costs. However, these frameworks do not incorporate simultaneous interactions between central bank balance sheets, signaling through issuance, and default incentives.

\paragraph{Endogenous Regime Outcomes Without Exogenous Switching.}

Finally, our framework generates regime-like outcomes endogenously. Inflation, sovereign risk, and policy interactions emerge from equilibrium behavior rather than from exogenous regime switching or Markov transitions.

This contrasts with regime-switching models such as \citet{DavigLeeper2007}, \citet{ChungDavigLeeper2007}, and \citet{BianchiMelosi2014,BianchiMelosi2019}, where policy regimes evolve exogenously. It also differs from learning models such as \citet{Bassetto2025}, where agents acquire information about fiscal fundamentals. 

Similarly, \citet{ArellanoBaiMihalache2025} generate sovereign risk dynamics through macroeconomic shocks and borrowing constraints rather than through endogenous signaling or equilibrium regime selection.

\medskip

Taken together, our framework combines:

\begin{itemize}
	\item Central bank balance sheet policies
	\item Endogenous nominal debt issuance
	\item Sovereign default risk
	\item Asymmetric information and signaling
	\item Monetary policy rules
\end{itemize}

While individual elements of this list appear in different strands of the literature, this combination has not been studied jointly in the informationally sensitive debt or monetary–fiscal interaction literature.


\subsection*{Result-Relevant Differences from Representative Approaches}

The seven papers discussed above are best viewed as representative of different approaches rather than as a single class of models with a common template. For that reason, the most useful comparison is not at the level of individual modeling details, but at the level of differences that materially change the economic mechanisms and therefore the results. The key distinction is that our framework combines nominal sovereign debt, default risk, central-bank balance-sheet policy, and asymmetric information in a single environment, so differences that may appear modular in the existing literature become jointly outcome-relevant in our setting.

\paragraph{Monetary policy affects debt markets through balance sheets, not only through rules or credibility.}
Several of the papers overlap with us in treating monetary policy as relevant for sovereign outcomes, but they typically do so through one channel at a time: an interest-rate rule as in \citet{ArellanoBaiMihalache2025}, regime credibility as in \citet{BianchiIlut2017} and \citet{BianchiMondragon2022}, distortionary money creation as in \citet{EspinoKozlowskiMartinSanchez2025}, or discretionary inflation as in \citet{HurtadoNunoThomas2022}. Our model instead gives monetary policy an additional effect through the central bank's own liabilities and asset holdings. Because reserves, reserve remuneration, bond purchases, and remittances all enter the fiscal authority's problem, monetary implementation changes debt valuation and repayment incentives directly, not only through macroeconomic conditions or policy expectations. This difference matters for results because it creates a channel through which balance-sheet composition itself changes bond prices, default probabilities, and inflation outcomes.

\paragraph{Debt issuance is informative in our model, whereas in the representative papers debt is usually priced, inherited, or chosen for other reasons.}
Many of the seven papers study debt pricing under default risk or inflation risk, and some of them allow debt to be chosen endogenously. However, the key difference is that our model makes issuance informative about hidden fiscal strength or repayment incentives. In most of the representative approaches, debt levels matter because they change repayment incentives, rollover exposure, inflationary temptation, or fiscal backing. In our setup, issuance also changes beliefs. That difference has first-order implications for results: debt prices can move not only because fundamentals deteriorate, but also because issuance changes the market's posterior about government type. As a result, the same increase in borrowing can have larger and more nonlinear effects on yields, inflation, and default risk than in models where debt is informative only through quantities and repayment arithmetic.

\paragraph{Financial segmentation changes who prices government debt and how policy passes through.}
Some overlap exists with papers that emphasize information heterogeneity or monetary frictions, but our segmentation mechanism is different. In our draft, banks have access to reserves while non-banks do not, and this segmentation becomes especially important when banks are risk averse. Then sovereign bonds are not priced by a representative investor under a single Euler equation; instead, bond yields embed a wedge between reserve remuneration and sovereign returns, and central-bank purchases operate through a portfolio-balance channel by removing risky debt from bank balance sheets. This difference matters because it changes the source of bond-price movements. In the representative papers above, bond spreads usually move because of default probabilities, policy-regime beliefs, or information acquisition. In our model, they can also move because monetary operations redistribute risk across sectors and alter the required risk premium.

\paragraph{Inflation and default are jointly determined through nominal liabilities and remittances.}
Several of the seven papers connect inflation and sovereign risk, but they do so in different ways: through fiscal backing and information sensitivity, through New Keynesian default amplification, through foreign-currency rollover crises, or through inflation as a partial default device. Our framework differs because nominal sovereign debt, central-bank remittances, and repayment/default choices are tied together in one nominal balance-sheet system. This means inflation is not merely a by-product of fiscal stress or an alternative to default; it changes the real burden of nominal obligations and also changes the value of central-bank transfers across repayment and default states. The implication is that inflation, debt pricing, and default are simultaneously linked through both government and central-bank balance sheets. Relative to the representative papers, this makes it more likely that modest policy changes or issuance changes generate state-dependent shifts in both pricing and repayment incentives.

\paragraph{Our framework can generate richer nonlinearities than models built around a single friction.}
Each of the seven papers isolates an important force: endogenous attention, heterogeneous information, regime beliefs, rollover multiplicity, external default in a New Keynesian model, distortionary domestic policies, or inflation as partial default. The overlap with our framework is therefore real, but partial. Our environment differs because several of these forces interact at once: asymmetric information affects issuance, issuance affects beliefs, beliefs affect default risk, default risk feeds back into inflation, and central-bank operations alter both prices and remittances. The resulting implication is not merely that our model has more ingredients, but that it can produce different comparative statics and stronger nonlinearities than frameworks where only one friction is active. In that sense, the main difference is not complexity for its own sake, but the possibility that monetary, fiscal, and informational channels reinforce each other in equilibrium.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\singlespacing
\bibliographystyle{plainnat}
\bibliography{sovereign_monetary_literature}

\end{document}



%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Comparison with Learning and Regime-Switching Models}

A large literature studies monetary–fiscal interactions through regime switching, learning, or expectations-driven dynamics. Standard regime-switching models such as \citet{DavigLeeper2007}, \citet{ChungDavigLeeper2007}, and \citet{BianchiMelosi2014,BianchiMelosi2019} assume that policy regimes evolve according to exogenous stochastic processes.

\citet{BianchiIlut2017} introduce uncertainty about fiscal and monetary regimes, while \citet{BianchiMondragon2022} emphasize credibility and rollover risk. \citet{bassetto2019inflation} introduce heterogeneous information, and \citet{Bassetto2025} introduce endogenous information acquisition.

These frameworks generate inflation and sovereign risk dynamics through belief changes about policy regimes or fiscal backing.


